### 2009-04-30 doc/tech_doc/storage_system/arc-storage-documentation.tex
Implemented Marek's comments

To manage collections the Bartender only needs to communicate with a Librarian service. To manage files it needs to communicate with Shepherd services as well. When a Bartender wants to create a new replica of a file (or the first replica of a new file) it should find available Shepherd services. The Bartender uses the list of Shepherd services registered to the Librarian.

@@

% section grid_integration (end)

>>>>

To manage collections the Bartender only needs to communicate with a Librarian service. To manage files it needs to communicate with Shepherd services as well. When a Bartender wants to create a new replica of a file (or the first replica of a new file) it should find available Shepherd services. The Bartender uses the list of Shepherd services registered to the Librarian, and chooses the locations of the replicas randomly from this list according a uniform distribution.

@@

The ARC DMC allows Grid jobs to access Chelonia directly. As long as A-REX, the job execution service of ARC, and ARC DMC are installed on a site, files can be both downloaded and uploaded by specifying the corresponding URL's in the job description. In this case, the Bartender URL needs to be embedded in the URL as a URL option. For example, if a job requires an input file \verb!/user/me/input.dat!, and a Bartender \verb!https://storage/Bartender! the URL specified in the job description will be as follows:
\begin{verbatim}
arc:///user/me/input.dat?BartenderURL=https://storage/Bartender
\end{verbatim}
% section grid_integration (end)
